Landscape composition and beneficial insects

### 2020-05-15 manuscript/manuscript_outline.Rmd
Added concurve terms back into model
- Need to figure out what to do about this. Is regularization enough?

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)

@@

@@

* _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (p = `r with(opilLinTerms, unboldRMD(p[loc=='Pivot']))`, `r with(opilLinTerms, unboldRMD(p[loc=='Wetland']))`)  
  + However, unlike _P. melanarius_ or _P. pardosa_, _P. opilio_ was not strongly influenced by any land cover type, except for Pasture (p = `r with(opilSmTerms,unboldRMD(p[Smoother=='ti(distMat,endDayMat):Pasture']))`)
  + This specific effect of pasture was not large, as the model using non-crop cover performed similarly ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod3)-AIC(mod4)))`)
  + In fact, both models that used landscape composition performed worse than the model with only trap location ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod3)))`,`r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod4)))`)

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(mgcv)

@@

#Get variance components
varComp <- rownames_to_column(data.frame(gam.vcomp(PteMelMod$mod3),spp='Pterostichus melanarius'),'term') %>% 
  bind_rows(rownames_to_column(data.frame(gam.vcomp(ParDisMod$mod3),spp='Pardosa distincta'),'term')) %>% 
  bind_rows(rownames_to_column(data.frame(gam.vcomp(OpilioMod$mod3),spp='Phalangium opilio'),'term')) %>%
  mutate(term=factor(term,levels=names(PteMelMod$mod3$sp)))

@@

* _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (p = `r with(opilLinTerms, unboldRMD(p[loc=='Pivot']))`, `r with(opilLinTerms, unboldRMD(p[loc=='Wetland']))`)  
  + However, unlike _P. melanarius_ or _P. pardosa_, _P. opilio_ was not strongly influenced by any land cover type, except for Pasture (p = `r with(opilSmTerms,unboldRMD(p[Smoother=='ti(distMat,endDayMat):Pasture']))`)
  + This effect of this specific land cover type was not very large, as the model using non-crop cover performed similarly ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod3)-AIC(mod4)))`)
  + In fact, the models that used landscape composition performed worse than the model with only trap location ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod3)))`,`r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod4)))`), indicating a weak effect of landscape composition
  + The temporal and spatial components, as in the other two species, were very strong (both p = `r with(opilSmTerms,unboldRMD(p[grepl('E,N',Smoother)]))`, and Easting

@@

```{r varComp, echo=FALSE, fig.cap='\\label{fig:varComp} Variance components of all models'}
ggplot(varComp,aes(x=term,y=std.dev))+geom_col()+theme_classic()+facet_wrap(~spp,ncol=1,scales='free_y')+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
```
